Contextual Combinatorial Cascading Bandits

### 2015-12-09 contextual combinatorial cascading bandits.tex
update comments

% my settings
\usepackage{amssymb,amsfonts,amsmath,bbm}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{bbm}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\usepackage{ifthen}
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames]{xcolor}

@@

\wei{This lemma needs to be clarified, using Lemma 4.6.
Also, our regret bound is expected regret but with a high probability? Sound a 
bit strange.}
\begin{lemma}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE\left[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE\left[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right].
\end{align*}
\end{lemma}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

@@

\begin{lemma} % det(V_t)
$\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
\end{lemma}
\begin{proof}
We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$, 
\wei{Why? need a citation?} and
\begin{align*}
&\trace(\bV_t)\\
& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
\end{align*}
\end{proof}

>>>>

% my settings
\usepackage{amssymb,amsfonts,amsmath,bbm}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\usepackage{ifthen}
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames]{xcolor}

@@

\wei{This lemma needs to be clarified, using Lemma 4.6.
Also, our regret bound is expected regret but with a high probability? Sound a 
bit strange.}
\shuai{Yes, our regret bound is expected regret with a high probability. The reason is that NIPS'11 gives such a result.}

Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. However, $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ is hard to estimate because $\bV_t$ only contains observed base arms. So we need the following lemma.
\begin{lemma}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$. Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
$$
E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE\left[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE\left[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right].
\end{align*}
\end{lemma}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

@@

\begin{lemma} % det(V_t)
$\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
\end{lemma}
\begin{proof}
Let the eigenvalues of $\bV_t$ be $\lambda_1, \ldots, \lambda_d > 0$. Then
$$
\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \leq  (\frac{\lambda_1 + \ldots + \lambda_d}{d})^d = (\trace(\bV_t)/d)^d.
$$
\wei{Why? need a citation?} \shuai{I have rewritten this part.}
Also,
\begin{align*}
&\trace(\bV_t)\\
& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
\end{align*}
\end{proof}
